Luminance constancy under fixed geometry

### 2018-02-06 Draft2/draft2.tex
more edits

@@

\subsection{Optimal receptive fields for luminance estimation have a center surround structure}
We used two supervised learning methods to learn the optimal receptive fields (RFs) for luminance estimation for the three types of variations in the spectral properties of the scene as discuss earlier. Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults}) shows the optimal RFs, the linear response of these RFs to the training dataset, and the estimates of the luminance of the target object in the test dataset for the three cases. We show the first two RFs obtained using the SVD and AMA methods (Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(a-b)). The RFs are ranked in ascending order of the value of the cost function. Thus the first RF corresponds to the direction along which the projection of the data gives the minimum cost. The L, M and S components give the weights for the linear sum of the cone responses for the three cone types. The salient features are: the center surround structure of the RFs and the higher weights of the L and M cones, compared to the S cones.

For case 1, since the illuminant and the background are fixed, all the information is in the central target object reflectance. Thus, the RFs weights are mostly concentrated around the center. For case 2, while the target and the illuminant spectra varies, the background object spectra is fixed. Hence, the luminance can be estimated by simply from the contrast between the response of the cones corresponding to the target and the background. Thus, while the RFs show a trend of weights concentrated at the center similar to case 1, there is large negative contribution from the surround. The spatial features of the RFs are due the stereotypical geometry of the images (see \nameref{Methods}). For case 3, has a similar center surround structure with more prominent features of the background, as we also vary the spectra of the background objects. Again, the spatial features are a result of the stereotypical geometry of the images.

@@

% Figure 13
\begin{figure}
\centering
\begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
	\caption{Case 1}
	\label{fig:case1Bar}
    \end{subfigure}
    ~ 
    \begin{subfigure}{0.22 \textwidth}   
	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
	\caption{Case 2}
	\label{fig:case2Bar}
    \end{subfigure}
    ~ 
        \begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
	\caption{Case 3}
	\label{fig:case3Bar}
    \end{subfigure}
    ~ 
        \begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_d.pdf}
	\caption{Case 4}
	\label{fig:case4Bar}
    \end{subfigure}
\caption{{\bf Error comparison across models:} Comparison of optimal AMA receptive fields from one case on the images of other cases. (a) Relative error of the estimates obtained using the linear model and AMA. The AMA receptive fields of case 1, 2 and 3 are used to estimate the target object luminance of the test images from case 1. The AMA receptive fields from all three cases perform well in this case. (b) Relative error for images of case 2. As expected, the error of the linear model on the center pixel is higher than AMA. AMA receptive fields from case 1 do worse than the receptive fields from case 2 and 3. (c) Relative error for images of case 3. The best predictions are from the receptive learnt using the images of case 3.}
 \label{fig:barGraphs}
\end{figure}

\begin{align}
E_{\rm rel} = \sqrt{\left\langle\left(\frac{\hat{Y}-Y}{Y}\right)^2\right\rangle},
\end{align}
where $\hat{Y}$ corresponds to the estimated luminance and $Y$ to the assigned luminance. We use the first 8 RFs for luminance estimation ( see Fig.~\ref{fig:RMSEvsNFilters}).

>>>>

{\bf Error estimation:}
The error of the luminance estimates are quantified in terms of the relative error ($E_{\rm rel}$), defined as follows:
\begin{align}
E_{\rm rel} = \sqrt{\left\langle\left(\frac{\hat{Y}-Y}{Y}\right)^2\right\rangle},
\end{align}
where $\hat{Y}$ corresponds to the estimated luminance and $Y$ to the assigned luminance.

@@

\subsection{Optimal receptive fields for luminance estimation have a center surround structure}
% Figure 14
\begin{figure}
\centering
\begin{subfigure}{0.21 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
	\caption{Case 1}
	\label{fig:case1Filter}
    \end{subfigure}
    ~ ~ ~
    \begin{subfigure}{0.21 \textwidth}   
	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
	\caption{Case 2}
	\label{fig:case2Filter}
    \end{subfigure}
    ~ ~ ~
        \begin{subfigure}{0.21 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
	\caption{Case 3}
	\label{fig:case3Filter}
    \end{subfigure}
    ~ ~ ~
        \begin{subfigure}{0.21 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_d.pdf}
	\caption{Case 4}
	\label{fig:case4Filter}
    \end{subfigure}
\caption{{\bf AMA receptive fields:} The first two AMA receptive fields for the four cases studied in this work. The receptive fields show a center surround structure. The L and M filters have larger weight as luminance is essentially a function of the L and M cone isomerizations. The stereotypical pattern in the receptive fields of case 4 is due to the fixed geometry of the images.}
 \label{fig:AMAFilters}
\end{figure}

Fig.~{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for luminance estimation for the spectral variations studied in this work. The receptive fields are ranked in ascending order of the value of the cost function associated with them. Thus the first RF corresponds to the direction along which the projection of the data gives the minimum cost. The L, M and S components give the weights for the linear sum of the cone responses for the three cone types. The salient features are: the center surround structure of the RFs and the higher weights of the L and M cones, compared to the S cones.

For case 1, since the illuminant and the background are fixed, all the information is in the central target object reflectance. Thus, the RFs weights are mostly concentrated around the center. For case 2, where the target and the background spectra varies, most of the luminance information is still concentrated around the central target object. For case 3, while the target and the illuminant spectra varies, the background object spectra is fixed. Hence, the luminance can be estimated by simply from the contrast between the response of the cones corresponding to the target and the background. Thus, while the RFs show a trend of weights concentrated at the center similar to case 1, there is large negative contribution from the surround. The spatial features of the RFs are due the stereotypical geometry of the images (see \nameref{Methods}). Case 4 has a similar center surround structure, but with more prominent features of the background since the spectra of the background objects are also varying. Again, the spatial features are a result of the stereotypical geometry of the images.

@@

% Figure 14
\begin{figure}
\centering
\begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
	\caption{Case 1}
	\label{fig:case1Bar}
    \end{subfigure}
    ~ 
    \begin{subfigure}{0.22 \textwidth}   
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
	\caption{Case 2}
	\label{fig:case2Bar}
    \end{subfigure}
    ~ 
        \begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
	\caption{Case 3}
	\label{fig:case3Bar}
    \end{subfigure}
    ~ 
        \begin{subfigure}{0.22 \textwidth}
	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_d.pdf}
	\caption{Case 4}
	\label{fig:case4Bar}
    \end{subfigure}
\caption{{\bf Error comparison across models:} Comparison of optimal AMA receptive fields from one case on the images of other cases. (a) Relative error of the estimates obtained using the linear model and AMA. The AMA receptive fields of case 1, 2 and 3 are used to estimate the target object luminance of the test images from case 1. The AMA receptive fields from all three cases perform well in this case. (b) Relative error for images of case 2. As expected, the error of the linear model on the center pixel is higher than AMA. AMA receptive fields from case 1 do worse than the receptive fields from case 2 and 3. (c) Relative error for images of case 3. The best predictions are from the receptive learnt using the images of case 3.}
 \label{fig:barGraphs}
\end{figure}
